Large-scale text pre-training helps with dialogue act recognition, but not without fine-tuning

### 2021-05-07 reports/IWCS2021/iwcs-short-paper.tex
small reference changes

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

@@

\footnotetext{\citet{Ravi2018}} % Not sure whether I really trust this SotA. I doesn't even use dialogue context as far as I can tell and this person https://github.com/glicerico/SGNN says they tried to replicate it and could only get %71.3 accuracy.

@@

%\appendix

>>>>

\usepackage{graphicx}
\usepackage{placeins}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\author{
  Bill Noble  \and  Vladislav Maraev\\ 
  Centre for Linguistic Theory and Studies in Probability\\%
  Department of Philosophy, Linguistics and Theory of Science\\%
  University of Gothenburg\\
  \texttt{\{bill.noble,vladislav.maraev\}@gu.se} \\
  \\
}

@@

\footnotetext{\citet{Kozareva2019}}

@@

\input{iwcs-short-paper-appendix}
